---
title: "Searching frequency"
author: "Hsieh M.H"
date: "2021/8/5"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(osfr)
library(plotly)  # 製造互動式統計圖
library(cowplot)  # 製造組合式統計圖
install.packages(dataskills)
```

匯入原始文獻資料
### 下載原始資料映像檔

```{r echo=TRUE, message=FALSE, warning=FALSE}
## Download and load W1 rawdata from OSF
osf_retrieve_file("he2v7") %>%
  osf_download()
## Download and load W2 rawdata from OSF
osf_retrieve_file("ch68a") %>%
  osf_download() 
```
### 載入原始資料物件

```{r message=FALSE, warning=FALSE}
load(list.files(recursive = TRUE,full.names = TRUE,include.dirs = TRUE,pattern = "*.Rdata")[1])
load(list.files(recursive = TRUE,full.names = TRUE,include.dirs = TRUE,pattern = "*.Rdata")[2])
ls()
file.remove(list.files(recursive = TRUE,full.names = TRUE,include.dirs = TRUE,pattern = "*.Rdata"))
```
### Wave 1原始資料欄位說明清單

```{r}
items %>% rmarkdown::paged_table(options = list(rows.print = 20))
```
### Wave 2 原始資料欄位說明清單

```{r}
tag_info %>% rmarkdown::paged_table(options = list(rows.print = 20))
```

### Wave 1 正式分析資料

根據以下描述，篩選納入正式分析的資料：

"Five hundred and twenty-six respondents completed the Wave 1 survey via the Prolific.com platform. Sixteen respondents were excluded for spending too much time on the survey("Duration..in.seconds." -> "Q1T_Page.Submit"). Another nine respondents were excluded for failing the catch question("Q1_CATCH1")."

由於初次嘗試發現分組人數與論文不一致，聯絡論文第一作者Arnout Boot，得知16位被排除的參與者是根據完成"Knowledge Test"的秒數。

```{r message=FALSE, warning=FALSE}
## check the equality of two data sets
sum(data_factors$Q1T_Page.Submit != data_numeric$Q1T_Page.Submit)
## Boxplot for test duration
boxplot(data_numeric$Q1T_Page.Submit)

wave1_rawdata <- data_numeric %>% 
## exclude the participants who spent more than 999 seconds on the knowledge test
  filter(Q1T_Page.Submit < 999) %>%
## exclude the participants who failed the catch question
  filter(Q1_CATCH1 == 5) %>%
## ## exclude the participants who spent time on the knowledge test longer than 3.29 standardized time
  filter(scale(Q1T_Page.Submit)<3.29)
## How many participants' data are analyzed?
wave1_rawdata %>%
  summarise(N=n())
```

```{r}
#嘗試用tibble做表單

Q12_Pinlu <- tibble(
            frequency = rep(c("Never", "Once every few days", "Once a day", "Once per hour", "Multiple times per hour"),c(12,51,225,98,14)),
                score = c("1","2","3","4","5")
            )
```


```{r}
  wave1_rawdata %>%
  select(ID,Q12) %>%
  pivot_longer(cols = starts_with("Q12"), names_to = "Fig3_", values_to = "rating") %>%
  group_by(ID) %>%
  summarise(Fig3_MultipleTimesPerHour_5 = mean(rating == 5),
                     Fig3_OncePerHour_4 = mean(rating == 4),
                        Fig3_OnceADay_3 = mean(rating == 3),
                Fig3_OnceEveryFewDays_2 = mean(rating == 2),
                           Fig3_Never_1 = mean(rating == 1)) %>%
  pivot_longer(cols = starts_with("Fig3_"), names_to = "Options", values_to = "Percentage") %>%
  group_by(Options) %>%
  arrange(desc(Options))
```

```{r}
##指定Media_use_frequency為Q12 Wave1_rawdata的某一項資料
Media_use_frequency <- wave1_rawdata %>%
  select(ID,Q12) %>%
  pivot_longer(cols = starts_with("Q12"), names_to = "Fig3_", values_to = "rating") %>%
  group_by(ID) %>%
  summarise(Fig3_MultipleTimesPerHour_5 = mean(rating == 5),
                     Fig3_OncePerHour_4 = mean(rating == 4),
                        Fig3_OnceADay_3 = mean(rating == 3),
                Fig3_OnceEveryFewDays_2 = mean(rating == 2),
                           Fig3_Never_1 = mean(rating == 1)) %>%
  pivot_longer(cols = starts_with("Fig3_"), names_to = "Options", values_to = "Percentage") %>%
  group_by(Options) %>%
  arrange(desc(Options))
```

#設定Fig3的基本布局
```{r}
Media_use_f <- aes(x = time, 
               y = score , 
               colour = group, 
               fill = group)
ggplot(data = wave1_rawdata, mapping = mapping)

```


