---
title: "descriptive statistics"
author: "Hsieh M.H"
date: "2021/7/31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(osfr)
```

### 下載原始資料映像檔

```{r echo=TRUE, message=FALSE, warning=FALSE}
## Download and load W1 rawdata from OSF
osf_retrieve_file("he2v7") %>%
  osf_download()
## Download and load W2 rawdata from OSF
osf_retrieve_file("ch68a") %>%
  osf_download() 
```

### 載入原始資料物件

```{r message=FALSE, warning=FALSE}
load(list.files(recursive = TRUE,full.names = TRUE,include.dirs = TRUE,pattern = "*.Rdata")[1])
load(list.files(recursive = TRUE,full.names = TRUE,include.dirs = TRUE,pattern = "*.Rdata")[2])
ls()
file.remove(list.files(recursive = TRUE,full.names = TRUE,include.dirs = TRUE,pattern = "*.Rdata"))
```

### Wave 1原始資料欄位說明清單

```{r}
items %>% rmarkdown::paged_table(options = list(rows.print = 20))
```
```
Q1: 第一波疫情資訊可信度評分 = Table 3
Q2~Q7: 參與者背景資訊調查
Q8~Q10: 媒體使用習慣調查 => Figure 2
Q12,Q14,Q15: 疫情資訊更新管道及頻率 => Table4, Figure 3, Table 5
Q16: Need for Cognition scale
Q17: Need for Cognitive Closure scale
```
### Wave 1 正式分析資料

根據以下描述，篩選納入正式分析的資料：

"Five hundred and twenty-six respondents completed the Wave 1 survey via the Prolific.com platform. Sixteen respondents were excluded for spending too much time on the survey("Duration..in.seconds." -> "Q1T_Page.Submit"). Another nine respondents were excluded for failing the catch question("Q1_CATCH1")."

由於初次嘗試發現分組人數與論文不一致，聯絡論文第一作者Arnout Boot，得知16位被排除的參與者是根據完成"Knowledge Test"的秒數。

```{r message=FALSE, warning=FALSE}
## check the equality of two data sets
sum(data_factors$Q1T_Page.Submit != data_numeric$Q1T_Page.Submit)
## Boxplot for test duration
boxplot(data_numeric$Q1T_Page.Submit)

wave1_rawdata <- data_numeric %>% 
## exclude the participants who spent more than 999 seconds on the knowledge test
  filter(Q1T_Page.Submit < 999) %>%
## exclude the participants who failed the catch question
  filter(Q1_CATCH1 == 5) %>%
## ## exclude the participants who spent time on the knowledge test longer than 3.29 standardized time
  filter(scale(Q1T_Page.Submit)<3.29)
## How many participants' data are analyzed?
wave1_rawdata %>%
  summarise(N=n())
```

重製原始論文 Table 3描述統計(預備搬移到“第一波疫情資訊可信度重製分析”)
###重製原始論文統計資料數據 
Table 3 描述統計(預備搬移到“第一波疫情資訊可信度重製分析”)
```{r approach01}
## True statement "I am sure this is true"

## Approach 1, my favor
wave1_rawdata %>%
  select(ID,Q1_1:Q1_12) %>%
  pivot_longer(cols = starts_with("Q1_"), names_to = "True_statment", values_to = "rating") %>%
  group_by(ID) %>%
  summarise(True_statement_5 = mean(rating == 5),
            True_statement_4 = mean(rating == 4),
            True_statement_3 = mean(rating == 3),
            True_statement_2 = mean(rating == 2),
            True_statement_1 = mean(rating == 1)) %>%
  pivot_longer(cols = starts_with("True_statement_"), names_to = "Options",values_to = "Percentage") %>%
  group_by(Options) %>%
  summarise(Mean = round(mean(Percentage)*100,1), 
            SD = round(sd(Percentage)*100,1),
            CI_L = round(Mean + qnorm(.025)*SD/sqrt(length(unique(ID))),1),
            CI_U = round(Mean + qnorm(.975)*SD/sqrt(length(unique(ID))),1),
            MIN = min(Percentage),
            MAX = max(Percentage)) %>%
  arrange(desc(Options))
```

```{r}
# False statement

# Approach 1, my favor
wave1_rawdata %>%
  select(ID,Q1_13R:Q1_24R) %>%
  pivot_longer(cols = starts_with("Q1_"), names_to = "False_statement", values_to = "rating") %>%
  group_by(ID) %>%
  summarise(False_statement_5 = mean(rating == 5),
            False_statement_4 = mean(rating == 4),
            False_statement_3 = mean(rating == 3),
            False_statement_2 = mean(rating == 2),
            False_statement_1 = mean(rating == 1)) %>%
  pivot_longer(cols = starts_with("False_statement"), names_to = "Options", values_to = "Percentage") %>%
  group_by(Options) %>%
   summarise(Mean = round(mean(Percentage)*100,1), 
            SD = round(sd(Percentage)*100,1),
            CI_L = round(Mean + qnorm(.025)*SD/sqrt(length(unique(ID))),1),
            CI_U = round(Mean + qnorm(.975)*SD/sqrt(length(unique(ID))),1),
            MIN = min(Percentage),
            MAX = max(Percentage)) %>%
  arrange(desc(Options))
```

```{r}
# Conspiracy statement

# Approach 1, my favor
   wave1_rawdata %>%
   select(ID,Q1_1CONSR:Q1_7CONSR) %>%
   pivot_longer(cols = starts_with("Q1_"), names_to = "Conspiracy_Rejection", values_to = "rating") %>%
  group_by(ID) %>%
   summarise(Conspiracy_statement_5 = mean(rating == 5),
             Conspiracy_statement_4 = mean(rating == 4),
             Conspiracy_statement_3 = mean(rating == 3),
             Conspiracy_statement_2 = mean(rating == 2),
             Conspiracy_statement_1 = mean(rating == 1)) %>%
  pivot_longer(cols = starts_with("Conspiracy_statement_"),
               names_to = "Options", values_to = "Percentage") %>% 
  group_by(Options) %>%
   summarise(Mean = round(mean(Percentage)*100,1), 
            SD = round(sd(Percentage)*100,1),
            CI_L = round(Mean + qnorm(.025)*SD/sqrt(length(unique(ID))),1),
            CI_U = round(Mean + qnorm(.975)*SD/sqrt(length(unique(ID))),1),
            MIN = min(Percentage),
            MAX = max(Percentage)) %>%
  arrange(desc(Options))
```
```{r}
# Negated conspiracy statement

# Approach 1, my favor
  wave1_rawdata %>%
  select(ID,Q1_8CONS) %>%
  pivot_longer(cols = starts_with("Q1_"), names_to = "Negated_ conspiracy_statement", values_to = "rating") %>%
  group_by(ID) %>%
  summarise(Negated_conspiracy_statement_5 = mean(rating == 5),
            Negated_conspiracy_statement_4 = mean(rating == 4),
            Negated_conspiracy_statement_3 = mean(rating == 3),
            Negated_conspiracy_statement_2 = mean(rating == 2),
            Negated_conspiracy_statement_1 = mean(rating == 1)) %>%
  pivot_longer(cols = starts_with("Negated_conspiracy_statement_"), names_to = "Options", values_to = "Percentage") %>%
  group_by(Options) %>%
  summarise(Mean = round(mean(Percentage)*100,1), 
            SD = round(sd(Percentage)*100,1),
            CI_L = round(Mean + qnorm(.025)*SD/sqrt(length(unique(ID))),1),
            CI_U = round(Mean + qnorm(.975)*SD/sqrt(length(unique(ID))),1),
            MIN = min(Percentage),
            MAX = max(Percentage)) %>%
  arrange(desc(Options))
```

