---
title: "news encounters"
author: "Hsieh M.H"
date: "2021/8/2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(osfr)
```

### 下載原始資料映像檔

```{r echo=TRUE, message=FALSE, warning=FALSE}
## Download and load W1 rawdata from OSF
osf_retrieve_file("he2v7") %>%
  osf_download()
## Download and load W2 rawdata from OSF
osf_retrieve_file("ch68a") %>%
  osf_download() 
```

### 載入原始資料物件

```{r message=FALSE, warning=FALSE}
load(list.files(recursive = TRUE,full.names = TRUE,include.dirs = TRUE,pattern = "*.Rdata")[1])
load(list.files(recursive = TRUE,full.names = TRUE,include.dirs = TRUE,pattern = "*.Rdata")[2])
ls()
file.remove(list.files(recursive = TRUE,full.names = TRUE,include.dirs = TRUE,pattern = "*.Rdata"))
```

### Wave 1原始資料欄位說明清單

```{r}
items %>% rmarkdown::paged_table(options = list(rows.print = 20))
```
```
Q1: 第一波疫情資訊可信度評分 = Table 3
Q2~Q7: 參與者背景資訊調查
Q8~Q10: 媒體使用習慣調查 => Figure 2
Q12,Q14,Q15: 疫情資訊更新管道及頻率 => Table4, Figure 3, Table 5
Q16: Need for Cognition scale
Q17: Need for Cognitive Closure scale
```
### Wave 1 正式分析資料

根據以下描述，篩選納入正式分析的資料：

"Five hundred and twenty-six respondents completed the Wave 1 survey via the Prolific.com platform. Sixteen respondents were excluded for spending too much time on the survey("Duration..in.seconds." -> "Q1T_Page.Submit"). Another nine respondents were excluded for failing the catch question("Q1_CATCH1")."

由於初次嘗試發現分組人數與論文不一致，聯絡論文第一作者Arnout Boot，得知16位被排除的參與者是根據完成"Knowledge Test"的秒數。

```{r message=FALSE, warning=FALSE}
## check the equality of two data sets
sum(data_factors$Q1T_Page.Submit != data_numeric$Q1T_Page.Submit)
## Boxplot for test duration
boxplot(data_numeric$Q1T_Page.Submit)

wave1_rawdata <- data_numeric %>% 
## exclude the participants who spent more than 999 seconds on the knowledge test
  filter(Q1T_Page.Submit < 999) %>%
## exclude the participants who failed the catch question
  filter(Q1_CATCH1 == 5) %>%
## ## exclude the participants who spent time on the knowledge test longer than 3.29 standardized time
  filter(scale(Q1T_Page.Submit)<3.29)
## How many participants' data are analyzed?
wave1_rawdata %>%
  summarise(N=n())
```

重製Table 4 
```{r}
# I actively search for updates about the coronavirus
wave1_rawdata %>%
 select(ID,Q10_1.1) %>%
 pivot_longer(cols = starts_with("Q10_1"), names_to = "Table4.1_", values_to = "rating") %>% 
 group_by(ID) %>%
 summarise(Table4.1_5_StronglyAgree = mean(rating == 5), 
           Table4.1_4_SomewhatAgree = mean(rating == 4), 
 Table4.1_3_NeitherAgreeNorDisagree = mean(rating == 3), 
        Table4.1_2_SomewhatDisagree = mean(rating == 2),
        Table4.1_1_StronglyDisagree = mean(rating == 1)) %>%
 pivot_longer(cols = starts_with("Table4.1_"), names_to = "Options", values_to = "Percentage") %>%
 group_by(Options) %>% 
 summarise(Mean = round(mean(Percentage)*100,1)) %>% 
 arrange(desc(Options))

#I coincidentally read news about the coronavirus when I`m browsing online
 wave1_rawdata %>%
 select(ID,Q10_2.1) %>%
 pivot_longer(cols = starts_with("Q10_2"), names_to = "Table4.2_", values_to = "rating") %>% 
 group_by(ID) %>%
 summarise(Table4.2_5_StronglyAgree = mean(rating == 5), 
           Table4.2_4_SomewhatAgree = mean(rating == 4), 
 Table4.2_3_NeitherAgreeNorDisagree = mean(rating == 3), 
        Table4.2_2_SomewhatDisagree = mean(rating == 2),
        Table4.2_1_StronglyDisagree = mean(rating == 1)) %>%
 pivot_longer(cols = starts_with("Table4.2_"), names_to = "Options", values_to = "Percentage") %>%
 group_by(Options) %>% 
 summarise(Mean = round(mean(Percentage)*100,1)) %>% 
 arrange(desc(Options))
 
 # I get updates about the coronavirus from other people (friends, family, coworkers)
 wave1_rawdata %>%
 select(ID,Q10_3.1) %>%
 pivot_longer(cols = starts_with("Q10_3"), names_to = "Table4.3_", values_to = "rating") %>% 
 group_by(ID) %>%
 summarise(Table4.3_5_StronglyAgree = mean(rating == 5), 
           Table4.3_4_SomewhatAgree = mean(rating == 4), 
 Table4.3_3_NeitherAgreeNorDisagree = mean(rating == 3), 
        Table4.3_2_SomewhatDisagree = mean(rating == 2),
        Table4.3_1_StronglyDisagree = mean(rating == 1)) %>%
 pivot_longer(cols = starts_with("Table4.3_"), names_to = "Options", values_to = "Percentage") %>%
 group_by(Options) %>% 
 summarise(Mean = round(mean(Percentage)*100,1)) %>% 
 arrange(desc(Options))
 # I ignore news about the coronavirus
 wave1_rawdata %>%
 select(ID,Q10_4.1) %>%
 pivot_longer(cols = starts_with("Q10_4"), names_to = "Table4.4_", values_to = "rating") %>% 
 group_by(ID) %>%
 summarise(Table4.4_5_StronglyAgree = mean(rating == 5), 
           Table4.4_4_SomewhatAgree = mean(rating == 4), 
 Table4.4_3_NeitherAgreeNorDisagree = mean(rating == 3), 
        Table4.4_2_SomewhatDisagree = mean(rating == 2),
        Table4.4_1_StronglyDisagree = mean(rating == 1)) %>%
 pivot_longer(cols = starts_with("Table4.4_"), names_to = "Options", values_to = "Percentage") %>%
 group_by(Options) %>% 
 summarise(Mean = round(mean(Percentage)*100,1)) %>% 
 arrange(desc(Options))
```




