---
title: "Straight from the scientist's mouth - Plain language summaries promote laypeople's comprehension and knowledge acquisition when reading about individual research findings in psychology: Code"
author: "Martin Kerwer"
date: "September 21, 2020"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
  word_document:
    toc: yes
    toc_depth: '3'
---


<!-- more -->
# SessionInfo


```{r echo=TRUE, message=TRUE, warning=TRUE, include=T, results='show'}

sessionInfo()

```

# Read Data


```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}


df <- read.csv("Gesamtdatensatz_Total_Dataset_Matrix.csv", na.strings = c("-999"))


df_wiss <- read.csv("Wissenstestdatensatz_Knowledge_Test_Dataset_Matrix.csv", na.strings = c("-999"))


```



# Confirmatory Analyses

## H1 Comprehensibility

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}



df$PLS <- factor(df$PLS, levels = c("PLS", "No Heading", "Non PLS"))

df$NH <- df$PLS == "No Heading"
df$OSA <- df$PLS == "Non PLS"


require(lme4)
require(lmerTest)
require(sjstats)
require(MuMIn)
library(multcomp)



m0 <- lmer(vst ~ (1 | id), data = df)
m00 <- lmer(vst ~ (1 | study), data = df)

#ICC Subject
summary(m0)
performance::icc(m0)

#ICC Study
summary(m00)
performance::icc(m00)


m1 <- lmer(vst ~ (1 | study) +PLS + (1 | id), data = df)

summary(m1)


test = glht(m1,linfct=mcp(PLS="Tukey"))
summary(test, test = adjusted("none"))



r.squaredGLMM(m1)



```

## H2 Knowledge Test

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}



names(df_wiss)



table(df_wiss$test)
table(df_wiss$test)/sum(table(df_wiss$test))
table(df_wiss$test, df_wiss$PLS)[1,]/colSums(table(df_wiss$test, df_wiss$PLS))
table(df_wiss$test, df_wiss$PLS)[2,]/colSums(table(df_wiss$test, df_wiss$PLS))

df_wiss$PLS <- factor(df_wiss$PLS, levels = c("PLS", "No Heading", "Non PLS"))

m0 <- glmer(test ~ (1 | id), family = binomial("logit"), data = df_wiss)

summary(m0)


m <- glmer(test ~ (1 | study) + (1 | id), family = binomial("logit"), data = df_wiss)

summary(m)


m1 <- glmer(test ~ (1 | study) + PLS + (1 | id), family = binomial("logit"), data = df_wiss)
  

summary(m1)


m2 <- glmer(test ~ (1 | study/item) + PLS + (1 | id), family = binomial("logit"), data = df_wiss)
  

summary(m2)


anova(m0, m , m1, m2)


m1 <- glmer(test~ (1 | study/item) + PLS + (1 | id), family = binomial("logit"), data = df_wiss)
test = glht(m1,linfct=mcp(PLS="Tukey"))
summary(test, test = adjusted("none"))


r.squaredGLMM(m1)


```


## H3 Credibility

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}


m0 <- lmer(vtr ~ (1 | id), data = df)
m00 <- lmer(vtr ~ (1 | study), data = df)

#ICC Subject
summary(m0)
performance::icc(m0)

#ICC Study
summary(m00)
performance::icc(m00)



m1 <- lmer(vtr ~ (1 | study) +PLS + (1 | id), data = df)

summary(m1)

anova(m0, m1)

m1 <- lmer(vtr ~ (1 | study) +PLS + (1 | id), data = df)
test = glht(m1,linfct=mcp(PLS="Tukey"))
summary(test, test = adjusted("none"))



r.squaredGLMM(m1)



```

## H4 Ability to Evaluate

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}


m0 <- lmer(wahr ~ (1 | id), data = df)
m00 <- lmer(wahr ~ (1 | study), data = df)

#ICC Subject
summary(m0)
performance::icc(m0)

#ICC Study
summary(m00)
performance::icc(m00)


m1 <- lmer(wahr ~ (1 | study) +PLS + (1 | id), data = df)

summary(m1)


m1 <- lmer(wahr ~ (1 | study) +PLS + (1 | id), data = df)
test = glht(m1,linfct=mcp(PLS="Tukey"))
summary(test, test = adjusted("none"))



r.squaredGLMM(m1)


```

## H5 Ability to Make a Decision

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}


m0 <- lmer(ent ~ (1 | id), data = df)
m00 <- lmer(ent ~ (1 | study), data = df)

#ICC Subject
summary(m0)
performance::icc(m0)

#ICC Study
summary(m00)
performance::icc(m00)


m1 <- lmer(ent ~ (1 | study) +PLS + (1 | id), data = df)

summary(m1)

test = glht(m1,linfct=mcp(PLS="Tukey"))
summary(test, test = adjusted("none"))



r.squaredGLMM(m1)


```

# Exploratory

## Scientificness

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}


m0 <- lmer(wis ~ (1 | id), data = df)
m00 <- lmer(wis ~ (1 | study), data = df)

#ICC Subject
summary(m0)
performance::icc(m0)

#ICC Study
summary(m00)
performance::icc(m00)


m1 <- lmer(wis ~ (1 | study) +PLS + (1 | id), data = df)

summary(m1)

test = glht(m1,linfct=mcp(PLS="Tukey"))
summary(test, test = adjusted("none"))


r.squaredGLMM(m1)



```





## Curiosity

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}


m0 <- lmer(cur ~ (1 | id), data = df)
m00 <- lmer(cur ~ (1 | study), data = df)

#ICC Subject
summary(m0)
performance::icc(m0)

#ICC Study
summary(m00)
performance::icc(m00)

m1 <- lmer(cur ~ (1 | study) +PLS + (1 | id), data = df)

summary(m1)

test = glht(m1,linfct=mcp(PLS="Tukey"))
summary(test, test = adjusted("none"))


r.squaredGLMM(m1)


```


## Boredom

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}


m0 <- lmer(bor ~ (1 | id), data = df)
m00 <- lmer(bor ~ (1 | study), data = df)

#ICC Subject
summary(m0)
performance::icc(m0)

#ICC Study
summary(m00)
performance::icc(m00)


m <- lmer(bor ~ (1 | study)  + (1 | id), data = df)

anova(m,m00)
anova(m,m0)


m1a <- lmer(bor ~ (1 | study) +PLS + (1 | id), data = df)

summary(m1a)

m1 <- lmer(bor ~ (1 | study) +PLS + (1 | id), data = df, REML = F)
summary(m1)

anova(m,m1)


test = glht(m1,linfct=mcp(PLS="Tukey"))
summary(test, test = adjusted("none"))


r.squaredGLMM(m1)




```

## Confusion

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}


m0 <- lmer(con ~ (1 | id), data = df)
m00 <- lmer(con ~ (1 | study), data = df)

#ICC Subject
summary(m0)
performance::icc(m0)

#ICC Study
summary(m00)
performance::icc(m00)


m1 <- lmer(con ~ (1 | study) +PLS + (1 | id), data = df)

summary(m1)

test = glht(m1,linfct=mcp(PLS="Tukey"))
summary(test, test = adjusted("none"))


r.squaredGLMM(m1)



```

## Frustration

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}



m0 <- lmer(frust ~ (1 | id), data = df)
m00 <- lmer(frust ~ (1 | study), data = df)

#ICC Subject
summary(m0)
performance::icc(m0)

#ICC Study
summary(m00)
performance::icc(m00)


m1 <- lmer(frust ~ (1 | study) +PLS + (1 | id), data = df)

summary(m1)


test = glht(m1,linfct=mcp(PLS="Tukey"))
summary(test, test = adjusted("none"))

r.squaredGLMM(m1)




```





## Full Text Access

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}

table(df$link)
table(df$link)/sum(table(df$link))

sum(table(df$link, df$id)[2,] > 0)
sort(table(df$link, df$id)[2,])
table(df$link, df$study)


table(df$link, df$PLS)
table(df$link, df$PLS)[1,]/colSums(table(df$link, df$PLS))
table(df$link, df$PLS)[2,]/colSums(table(df$link, df$PLS))





m1 <- glmer(link ~ (1 | study) + PLS + (1 | id), family = binomial("logit"), data = df)
  

summary(m1)

test = glht(m1,linfct=mcp(PLS="Tukey"))
summary(test, test = adjusted("none"))


r.squaredGLMM(m1)


```


# Model Tests Interindividuell Differences


## Comprehensibility

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}


require(sjstats)
require(MuMIn)

# Random Intercepts

m00 <- lmer(vst ~ NH + OSA +(1 | study), data = df)

m1 <- lmer(vst ~(1 | study) + NH + OSA +  (1 | id), data = df)

anova(m00, m1)

# Random Slopes

m2a <- lmer(vst ~(1 | study) + NH + OSA +   (OSA | id), data = df)


m2b <- lmer(vst ~(1 | study) + NH + OSA +   (NH | id), data = df, REML = F)
summary(m2b)



anova(m2a, m1)
anova(m2b, m1)
summary(m2a)




m3a <- lmer(vst ~(1 | study) + NH+ OSA + j_ja   + j_pj + j_ms +   (OSA | id), data = df)
m3b <- lmer(vst ~(1 | study) + NH+ OSA * j_ja   + OSA * j_pj + OSA * j_ms +   (OSA | id), data = df)


anova(m2a,m3a)
anova(m2a,m3b)




summary(m3b)


m3a <- lmer(vst ~(1 | study) + NH+ OSA + Englisch +   (OSA | id), data = df)
m3b <- lmer(vst ~(1 | study) + NH+ OSA * Englisch +   (OSA | id), data = df)


anova(m2a,m3a)
anova(m3a,m3b)


summary(m3a)


```


## Knowledge Test


```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}

df_wiss$NH <- df_wiss$PLS == "No Heading"
df_wiss$OSA <- df_wiss$PLS == "Non PLS"

#Random Intercept

m00 <- glmer(test ~ NH + OSA +(1 | study/item), data = df_wiss, family = binomial("logit"))
m1 <- glmer(test ~ NH + OSA + (1 | study/item) + (1 | id), data = df_wiss, family = binomial("logit"))

anova(m00, m1)

m1 <- glmer(test ~ (1 | study/item) + NH + OSA  + (1 | id), data = df_wiss, family = binomial("logit"))

#non-convergence
m2a <- glmer(test ~ (1 | study/item) + NH + OSA + (OSA | id), data = df_wiss, family = binomial("logit"))
summary(m2a)

m2b <- glmer(test ~ (1 | study/item) + NH + OSA + (NH | id), data = df_wiss, family = binomial("logit"))
summary(m2b)

anova(m1, m2b)

m3 <- glmer(test ~ (1 | study/item) + NH + OSA + j_pj + j_ja + j_ms  + (1 | id), data = df_wiss, family = binomial("logit"))

anova(m1, m3)


summary(m3)


m3 <- glmer(test ~ (1 | study/item) + NH + OSA + Englisch + (1 | id), data = df_wiss, family = binomial("logit"))

anova(m1, m3)


summary(m3)


```

## Credibility

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}



#Random Intercept

m00 <- lmer(vtr ~ NH + OSA + (1 | study), data = df)

m <- lmer(vtr ~ NH + OSA + (1 | study) +  (1 | id), data = df)

anova(m00, m)

#Random Slopes

m2a <- lmer(vtr ~(1 | study) + NH + OSA +   (OSA | id), data = df)

m2b <- lmer(vtr ~(1 | study) + NH + OSA +   (NH | id), data = df)
m2b <- lmer(vtr ~(1 | study) + NH + OSA +   (NH | id), data = df, REML = F)

summary(m2b)


anova(m2a, m)
anova(m2b,m)

summary(m2a)


m3a <- lmer(vtr ~(1 | study) + NH + OSA + j_ja   + j_pj +  j_ms +   (OSA | id), data = df)
m3b <- lmer(vtr ~(1 | study) + NH + OSA * j_ja   + OSA * j_pj + OSA * j_ms +   (OSA | id), data = df)

anova(m2a,m3a,m3b)

summary(m3a)


#non-convergence
m3a <- lmer(vtr ~(1 | study) + NH+ OSA + Englisch +   (OSA | id), data = df, REML = F)
m3b <- lmer(vtr ~(1 | study) + NH+ OSA * Englisch +   (OSA | id), data = df)


anova(m2a,m3a, m3b)
anova(m2a,m3b)



```




## Ability to Evaluate

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}


# Random Intercept

m00 <- lmer(wahr ~ NH + OSA + (1 | study), data = df)

m <- lmer(wahr ~ NH + OSA + (1 | study) +  (1 | id), data = df)

anova(m00, m)

# Random Slopes

m2a <- lmer(wahr ~(1 | study) + NH + OSA +   (OSA | id), data = df)

#non-convergence
m2b <- lmer(wahr ~(1 | study) + NH + OSA +   (NH | id), data = df, REML = T)
m2b <- lmer(wahr ~(1 | study) + NH + OSA +   (NH | id), data = df, REML = F)
summary(m2b)


anova(m2a, m)
summary(m2a)


m3a <- lmer(wahr ~(1 | study) + NH + OSA + j_ja   + j_pj +  j_ms +   (OSA | id), data = df)
m3b <- lmer(wahr ~(1 | study) + NH + OSA * j_ja   + OSA * j_pj + OSA * j_ms +   (OSA | id), data = df)

anova(m2a,m3a,m3b)

summary(m3a)


m3a <- lmer(wahr ~(1 | study) + NH+ OSA + Englisch +   (OSA | id), data = df)
m3b <- lmer(wahr ~(1 | study) + NH+ OSA * Englisch +   (OSA | id), data = df)


anova(m2a,m3a)
anova(m2a,m3b)





```

## Ability to Make Decision

```{r, echo=TRUE, results='show', message=TRUE, warning=TRUE, include=T}

# Random Intercept

m00 <- lmer(ent ~ NH + OSA + (1 | study), data = df)

m <- lmer(ent ~ NH + OSA + (1 | study) +  (1 | id), data = df)

anova(m00, m)

# Random Slopes

# Non-convergence

m2a <- lmer(ent ~(1 | study) + NH + OSA +   (OSA | id), data = df)
m2a <- lmer(ent ~(1 | study) + NH + OSA +   (OSA | id), data = df, REML = F)

#converged nicht
m2b <- lmer(ent ~(1 | study) + NH + OSA +   (NH | id), data = df)
summary(m2b)
m2b <- lmer(ent ~(1 | study) + NH + OSA +   (NH | id), data = df, REML = F)
summary(m2b)

anova(m, m2b)

summary(m)


m3a <- lmer(ent ~(1 | study) + NH + OSA + j_ja   + j_pj +  j_ms +   (1 | id), data = df)


anova(m,m3a)

summary(m3a)


m3a <- lmer(ent ~(1 | study) + NH+ OSA + Englisch +   (1 | id), data = df)


anova(m,m3a)



```


